% Publication Title
\title{Optical Character Recognition of Ancient Scripts and Transliteration into Devanagari Script}

% Short title for the header (copy the main title if it is not too long)
\shorttitle{OCR and Transliteration of Ancient Scripts}
       
% Authors
\author[1]{Prof. Rohini P}
\author[2]{Yash Agarwal}
\author[2]{Srinidhi B}
\author[2]{Srikari S}
\author[2]{Rohail Alam}
\author[3]{Himanshu Malviya}
\author[4]{Rahul Meena}

% Author Affiliations
\affil[1]{Assistant Professor, Department of Electronics and Communication Engineering}
\affil[2]{Pre-Final Year Student, Electronics and Communication Engineering}
\affil[3]{Pre-Final Year Student, Computer Science Engineering}
\affil[4]{Pre-Final Year Student, Smart Manufacturing}

\affil[ ]{,Indian Institute of Information Technology Design and Manufacturing, Kancheepuram}


% Surname of the first author of the manuscript
\firstauthor{SurnameA, SurnameB and SurnameC}

%Contact Author Information
% \contactauthor{Name A. Surname}           % Name and surname of the contact author
% \email{name.surname@email.com}            % Contact Author Email

% Publication data (will be defined in the edition)
\thisvolume{XX}
\thisnumber{XX}
\thismonth{Month}
\thisyear{20XX}
\receptiondate{dd/mm/aaaa}
\acceptancedate{dd/mm/aaaa}
\publicationdate{dd/mm/aaaa}

% Place your particular definitions here
\newcommand{\vect}[1]{\mathbf{#1}}  % vectors

% Insert here the abstract in English language
\abstract{
This document provides a template for the preparation of original work whose authors wish to be published in the Academic Journal on Computing, Engineering and Applied Mathematics of the Universidade Federal do Tocantins Tocantins, Brazil. At first, we strongly recommend the summary to be written as a single paragraph containing at least 150 and at most 200 words. In this text section, it is expected a summary including the context, motivation, methodology, the most original contributions, results, and conclusions of your work. In addition, bibliographic citations, acronyms, or formulas should be avoided in the abstract as well as in the title. It is also strongly recommended to avoid any references to figures or tables in this section. Finally, it is a good practice to write your article by inserting text to and deleting from straight to/from this template file in order to maintain the predefined styles.}

% Insert here the keywords of your work in English language
\keywords{
First word or key phrase, second word or key phrase, third word or key phrase. (Place between three and six key words or phrases separated by a comma, which represent the theme of your work)}